Efficient Selection of Time Series Shapelets

### 2024-04-16 Docs/paper/main.tex
Drafting the approach

\begin{definition}[Silhouette score of a subsequence]
	Given a set $\mathcal{D}$ of subsequences (sliding windows) and their
	corresponding labels, the silhouette score for a subsequence $S_i$ having label
	$c$ is:
	$$
		s(S_i) = \frac{b - a}{\max{(a, b)}}
	$$
	where:
	\begin{itemize}
		\item $b = \frac{\sum_{j \in I \setminus I_c}d(S_i, S_j)}{|I \setminus I_c|}$,
		\item $a = \frac{\sum_{k \in I_c}d(S_i, S_k)}{|I_c|}$,
		\item $I$ is the set of indices of all subsequences in $\mathcal{D}$, and
		\item $I_c$ is the set of indices of subsequences having label $c$.
	\end{itemize}
\end{definition}

Notice, that our definition of the silhouette, the term $b$ considers all 
subsequences from other classes instead of only considering only the class that
is closest to the subsequence $S_i$.

%NN-Descent~\cite{NN-Descent} is based on the principle: \textit{A neighbor of
%a neighbor is likely to be a neighbor}. The idea is, given an approximation
%graph of the nearest neighbor, then the approximation can be improved,
%in an iterative fashion, by exploring the neighbors of the neighbors of each
%point. To improve the running time, the authors use local join to avoid
%comparing same points many times in the same iteration. They also use
%incremental search to avoid comparing points that have been compared in
%previous iterations. Also, sampled is used to lower the overhead of local
%joins. Finally, random projection trees are used to initialize the graph.

>>>>

\begin{definition}[Silhouette score of a subsequence]
	Given a set $\mathcal{D}$ of subsequences (sliding windows) and their
	corresponding labels, the silhouette score for a subsequence $S_i$ having label
	$c$ is:
	$$
		s(S_i) = \frac{b - a}{\max{(a, b)}}
	$$
	where:
	\begin{itemize}
		\item $a = \frac{\sum_{k \in I_c}d(S_i, S_k)}{|I_c|}$,
		\item $b = \frac{\sum_{j \in I \setminus I_c}d(S_i, S_j)}{|I \setminus I_c|}$,
		\item $I$ is the set of indices of all subsequences in $\mathcal{D}$, and
		\item $I_c$ is the set of indices of subsequences having label $c$.
	\end{itemize}
\end{definition}

Notice that our definition of the silhouette, the term $b$ considers all
subsequences from other classes instead of only considering only the class that
is closest to the subsequence $S_i$.

\section{Approach}
The bottleneck of the computation is in the evaluation part, where, in order to
compute the Silhouette score (also for the F-statistic and all other measures),
all pairs of distances have to be computed. To avoid that, we will use the fact
that shapelets that have a high silhouette score are of good quality for time
series classification. Since we know, in a clustering setup, silhouette is high
when he clusters are compact and far from each other, then the problem of
finding good quality shapelets reduces to finding clusters with high silhouette
scores.

We start by extracting the set of sliding windows $W$ from all the time series
$W = \bigcup_T W_T^l$, then we cluster all the windows in $W$.
For each cluster $C_i$, we assign a label $c$ using a majority vote, i.e., the
label of cluster $C_i$ is the label of the set with largest cardinal, consisting
of windows assigned to cluster $C_i$ that have the same class label.

\section{Experimental Evaluation}

\section{Conclusion}
